\documentclass[a4paper,10pt]{article}

% CV tailored for Revotronics Labs — R&D Power & Embedded Electronics
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{roboto}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\hypersetup{pageanchor=false}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{cmap}
\usepackage{xcolor}

% ── Color Palette ────────────────────────────────────────────────────────────
\definecolor{navyblue}{RGB}{18, 52, 86}

% ── Layout ───────────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=0.18in, topsep=2pt, itemsep=1.5pt, parsep=0pt}
\titleformat{\section}[block]{\large\bfseries\color{navyblue}}{}{0pt}{\MakeUppercase}[\color{navyblue}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{5pt}
\pagenumbering{gobble}
\raggedright


% Sub-project heading inside Experience: bold title (left) + small italic date (right)
\newcommand{\projectheading}[2]{%
  \vspace{4pt}\noindent\textbf{#1} \hfill \textit{\small #2}\\%
}


\begin{document}

% ═══════════════════════════════════════════════════════════════════════════════
%  HEADER
% ═══════════════════════════════════════════════════════════════════════════════
\begin{center}
  {\LARGE \textbf{\color{navyblue}Ahmed Ahmed}}\\
  \vspace{3pt}
  {\large \textbf{R\&D Power \& Embedded Electronics Engineer}}\\
  \vspace{4pt}
  \small
  Konya, Turkey
  \;\textbullet\;
  +90 552 313 55 38
  \;\textbullet\;
  \href{mailto:ahmedmikatronik@gmail.com}{ahmedmikatronik@gmail.com}
  \;\textbullet\;
  \href{https://www.linkedin.com/in/ahmedmekatronik/}{linkedin.com/in/ahmedmekatronik}
  \;\textbullet\;
  \href{https://github.com/Ahmed-mek/}{github.com/Ahmed-mek/}
\end{center}

\vspace{2pt}

% ═══════════════════════════════════════════════════════════════════════════════
%  PROFESSIONAL SUMMARY
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Professional Summary}
R\&D engineer with 5+ years delivering embedded power systems, motor-driver architectures, and
advanced PCBs for UAV and robotics applications. Proven track record across BLDC/ESC
development, SMPS and BMS design, 200W wireless power transfer, STM32 firmware on FreeRTOS,
and high-density KiCad PCB layout --- from concept through hardware validation.

Hands-on experience in government-funded R\&D (TUBITAK), academic UAV research,
electric-vehicle power systems, and industrial embedded platforms. Strong fit for Revotronics
Labs combining motor-driver design, power-conversion expertise, real-time firmware development,
and rigorous prototype-to-system delivery in demanding R\&D environments.

% ═══════════════════════════════════════════════════════════════════════════════
%  TECHNICAL SKILLS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Power Electronics:} Motor drivers, BLDC motors, ESCs, FOC, Space Vector PWM,
        Six-Step Commutation, PID control, buck/boost converters, gate drivers, SMPS, BMS,
        battery charging, wireless power transfer (200W WPT), galvanic isolation,
        high-current PCB design, power distribution, analog systems, ADC/DAC interfacing,
        IC selection, signal filtering, EMC considerations.
  \item \textbf{Embedded Firmware:} Embedded C/C++, bare-metal programming, FreeRTOS,
        FreeRTOS-MPU, FreeRTOS+TCP, deterministic task management, fault monitoring,
        real-time safety logic, DMA, UART, SPI, I2C, CAN, Modbus, SMBus, Ethernet,
        TCP/IP, SD-card data logging.
  \item \textbf{Microcontrollers \& Platforms:} STM32H7, STM32F7, STM32, RP2040, ESP32,
        Arduino, NEXTION HMI, ToF sensors, Multi-IMU sensor arrays.
  \item \textbf{PCB Design \& Hardware:} Schematic design, advanced KiCad PCB layout,
        Altium Designer, Eagle, KiCad plugin development, high-density LED PCB,
        power-management PCB design, oscilloscope, function generator, soldering,
        hardware validation and debugging.
  \item \textbf{UAV, Robotics \& Control:} UAV electronics, drone wireless charging,
        flight controller architecture, ArduPilot/PX4 analysis, robotics control systems,
        GPS-denied localization, Kalman Filtering, sensor fusion, ROS,
        embedded Linux (3+ years daily use).
  \item \textbf{Programming Languages:} C, C++, C\#, Python, MicroPython, JavaScript.
  \item \textbf{Languages:} Arabic (native), Turkish (advanced --- C1), English (advanced).
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
%  EXPERIENCE
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Experience}
\textbf{Zenopix Technology} \hfill Konya, Turkey\\
\textit{R\&D Embedded Systems Engineer} \hfill 2021--Present

% ── Project 1 ─────────────────────────────────────────────────────────────────
\projectheading{UAV Wireless Charging Station}{2026--Present \normalfont\small(Ongoing)}
\begin{itemize}
  \item Architected an integrated wireless charging platform for UAV applications, engineering
        ground transmitter (Tx) and onboard receiver (Rx) power electronics for autonomous
        drone charging cycles.
  \item Developed a custom BMS architecture for UAV battery packs covering safe charging
        profiles, real-time telemetry monitoring, battery-health optimization, and embedded
        fault handling via SMBus communication.
  \item Integrated power conversion, BMS, and embedded control requirements into an R\&D
        platform aligned with UAV wireless power transfer, SMPS, and firmware development
        objectives.
\end{itemize}

% ── Project 2 ─────────────────────────────────────────────────────────────────
\projectheading{Industrial BLDC Motor Driver}{2026--Present \normalfont\small(Ongoing)}
\begin{itemize}
  \item Defined the architectural framework for a robust industrial BLDC motor driver
        optimized for high-reliability operation in demanding electromechanical systems.
  \item Formulated motor-control design requirements covering drive stages, control-loop
        stability, protection logic, thermal robustness, gate driver selection, and
        firmware interfaces.
  \item Structured the hardware concept around FOC and Six-Step control, high-current PCB
        layout, buck/boost-stage considerations, and hardware validation planning.
\end{itemize}

% ── Project 3 ─────────────────────────────────────────────────────────────────
\projectheading{Hologram Fan System --- TUBITAK R\&D Project}{2024--2026}
\begin{itemize}
  \item Engineered a custom 0.5-meter high-density LED PCB for a Persistence of Vision
        display, selecting high-performance LEDs and driver ICs capable of high-frequency
        switching.
  \item Designed high-current KiCad PCBs with strict galvanic isolation between power
        electronics and high-speed control circuitry for safer operation and cleaner signal
        behavior.
  \item Implemented BLDC motor-control algorithms including FOC, Space Vector PWM,
        Six-Step Commutation, and PID loops to regulate speed stability and display
        synchronization.
  \item Architected STM32 firmware with FreeRTOS for deterministic task management,
        real-time safety monitoring, fault detection, error handling, and system recovery.
  \item Developed a resonance-based wireless power transfer system by designing customized
        Tx/Rx circuits and achieving continuous 200W power transmission.
  \item Applied Fuzzy Logic Control to dynamically regulate wireless power delivery and
        improve transfer stability under varying operating conditions.
  \item Validated power electronics, PCB assemblies, and embedded control behavior using
        oscilloscopes, function generators, rapid prototyping, soldering, and hands-on
        hardware debugging.
\end{itemize}

% ── Project 4 ─────────────────────────────────────────────────────────────────
\projectheading{End-to-End Control System --- Abrasion Tester Machine}{2021--2023}
\begin{itemize}
  \item Built the complete signal-processing pipeline for accurate sensor-data acquisition
        using digital filtering, analog filtering, and embedded measurement logic over SPI
        and I2C interfaces.
  \item Developed a custom DC motor driver with PID algorithms for accurate speed
        calibration and repeatable mechanical testing.
  \item Programmed a PC-based C\# graphical user interface to control the machine, monitor
        operating behavior, and log test data in real time via UART communication.
  \item Delivered the control-board hardware and firmware from concept through debugging,
        calibration, and operational validation.
\end{itemize}

% ── Project 5 ─────────────────────────────────────────────────────────────────
\projectheading{Embedded Interface Development \& UI Simulation}{2021--2022}
\begin{itemize}
  \item Developed an interactive JavaScript/CSS lighting simulation demonstrating
        environmental lighting effects for customer-facing product visualization.
  \item Launched four localized multilingual corporate websites and implemented SEO
        optimizations to improve online discoverability.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
%  PROJECTS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Projects}

\textbf{Indoor Unmanned Vehicle Localization for Drift Reduction Using Multi-IMU Sensor Fusion}
\hfill 2025--Present\\
\textit{Master's Thesis | Multi-IMU, Sensor Fusion, STM32H7, FreeRTOS, Kalman Filtering}
\begin{itemize}
  \item Built a high-performance embedded system using STM32H7 to process approximately
        250 raw data channels from a custom Multi-IMU hardware array in real time over
        SPI and I2C buses.
  \item Implemented FreeRTOS, FreeRTOS-MPU, and FreeRTOS+TCP for deterministic
        multitasking, memory protection, robust network communication, and scalable
        firmware architecture.
  \item Developed Kalman Filtering and sensor-fusion algorithms to estimate navigation
        states and reduce drift in GPS-denied UAV and robotics environments.
  \item Integrated DMA-driven data acquisition, Ethernet communication, and real-time
        processing into a research platform applicable to autonomous vehicles and embedded
        control.
\end{itemize}

\vspace{3pt}
\textbf{Flight Controller Architecture \& Prototyping --- ArduPilot / PX4}
\hfill 2025--Present\\
\textit{Project | ArduPilot, PX4, Flight Controller, PCB Design, Sensor Isolation}
\begin{itemize}
  \item Conducted architectural analysis and reverse engineering of ArduPilot and PX4
        flight stacks to define hardware, firmware, and communication protocol requirements
        for a custom UAV flight controller.
  \item Designed the first iteration of a custom flight-controller PCB with attention to
        sensor isolation, power distribution, component placement, and KiCad layout
        constraints.
  \item Formulated a bare-metal firmware strategy around control loops, sensor fusion,
        embedded safety behavior, and future UAV ecosystem compatibility.
\end{itemize}

\vspace{3pt}
\textbf{Laser Vibrometer PCB \& System Design} \hfill 2024\\
\textit{Freelance | PCB Design, Power Management, Sensors, Data Logging}
\begin{itemize}
  \item Designed a custom PCB with battery charging, power-management circuitry, precision
        laser control, and embedded measurement interfaces over I2C and UART.
  \item Integrated ToF sensor for accurate distance and vibration measurement in an
        embedded instrumentation platform.
  \item Developed PC communication protocols and high-speed SD-card data logging to
        support repeatable test capture and analysis.
\end{itemize}

\vspace{3pt}
\textbf{Temperature Control System --- Cosmetic Medical Device Furnace} \hfill 2023\\
\textit{Freelance | Embedded Systems, PCB Design, PID Control}
\begin{itemize}
  \item Designed the hardware layout and primary control PCB for a specialized medical
        thermal-control device.
  \item Implemented PID control algorithms to maintain accurate and stable furnace
        temperature regulation.
  \item Programmed an interactive NEXTION HMI interface for operator control and
        real-time monitoring via UART communication.
\end{itemize}

\vspace{3pt}
\textbf{International Efficiency Challenge Electric Vehicle Races --- Electromobile Category}
\hfill 2024--2025\\
\textit{Competition | Motor Driver, Power Supply, BMS, SMPS, EV}
\begin{itemize}
  \item Designed a motor driver for a 4.5\,kW, 72V BLDC motor used in an electric vehicle
        competition platform.
  \item Designed a 3\,kW power supply based on a 220V-to-72V AC transformer for
        induction-load inspection tests.
  \item Researched and supported Battery Management System (BMS) development for
        electric-vehicle energy storage and protection via CAN communication.
  \item Contributed to the design of a local charging unit applying SMPS topologies and
        power-conversion principles.
  \item Coordinated project delivery, technical execution, and team performance under
        competition deadlines.
\end{itemize}

\vspace{3pt}
\textbf{Hyperloop Development Competition} \hfill 2023\\
\textit{Competition | STM32F7, Ethernet, TCP/IP, Embedded Networking}
\begin{itemize}
  \item Designed a data-transmission system between the train and monitoring station using
        STM32F7 Ethernet capability and a TCP/IP stack.
  \item Deployed a TCP-based communication path through router and Wi-Fi infrastructure
        for computer-side monitoring.
  \item Validated embedded network communication concepts applicable to high-speed robotics
        and autonomous transportation systems.
\end{itemize}

\vspace{3pt}
\textbf{POSYAK Medical Assistive Device --- Barrier-Free Living Technologies} \hfill 2022\\
\textit{Competition | Wearable, Motion Sensing, Mobile App}
\begin{itemize}
  \item Developed a wearable assistive device for Parkinson's patients that generated
        posture alerts when neck remained bent beyond a defined duration threshold.
  \item Integrated I2C-based IMU motion-data collection with a mobile application to
        record and process head-movement behavior.
\end{itemize}

\vspace{3pt}
\textbf{Additional Engineering Competitions and Early Technical Projects} \hfill 2014--2024\\
\textit{Projects | UAV, Robotics, Embedded Systems, Education}
\begin{itemize}
  \item Contributed to a Fighting UAV Competition project, participating in unmanned aerial
        vehicle design and development tasks.
  \item Contributed to an Agricultural Unmanned Ground Vehicle Competition focused on
        autonomous ground-vehicle functionality for agricultural applications.
  \item Designed and built a rotary-wing UAV for the International UAV Competition with
        emphasis on agility, reliability, and embedded control efficiency.
  \item Guided younger participants as a technical consultant in a Smart Transportation
        Competition, supporting concept development and engineering execution.
  \item Built educational-technology and quiz software using C\#, database integration,
        authentication screens, scoring logic, and user-interface design.
  \item Achieved first place in a middle-school electronics competition by accurately
        assembling a random schematic circuit in the shortest time.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
%  EDUCATION
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Education}

\textbf{Necmettin Erbakan University} \hfill Konya, Turkey\\
Master's Degree, Mechatronics Engineering \hfill 2024--Present

\vspace{4pt}
\textbf{Necmettin Erbakan University} \hfill Konya, Turkey\\
Bachelor's Degree, Mechatronics Engineering \hfill 2020--2024\\
GPA: 3.06\,/\,4.00 \quad \textit{Graduated with Honours (Onur Belgesi)}

\vspace{4pt}
\textbf{TOMER} \hfill Istanbul, Turkey\\
Turkish Language Course, C1 Level \hfill 2019--2020

\vspace{4pt}
\textbf{AL KINDY High School} \hfill Kuwait\\
High School, Natural Sciences \hfill 2016--2019

% ═══════════════════════════════════════════════════════════════════════════════
%  CERTIFICATIONS & AWARDS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Certifications \& Awards}
\begin{itemize}
  \item International Efficiency Challenge Electric Vehicle --- Teknofest Finalist, 2025.
  \item International Efficiency Challenge Electric Vehicle --- Teknofest Finalist, 2024.
  \item Graduation with Honours (Onur Belgesi) --- Necmettin Erbakan University, 2024.
  \item Microcontroller Embedded C Programming: Absolute Beginners --- Udemy, 2023.
  \item Mastering RTOS: Hands-on FreeRTOS and STM32Fx with Debugging --- Udemy, 2023.
  \item Linux Training (Ubuntu) --- Komek, 2022.
  \item First Aid Certification --- Komek, 2022.
  \item Arduino Programming and Development Course --- Komek, 2021.
\end{itemize}

\end{document}
